Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-09 paper/paper.tex
Include turning function plots in report
Report todo
Report abstract

@@

% TODO: Turning function overlap, example figure with two polygos

>>>>

This project assesses the feasibility of creating a 3D representation of geodata with the inclusion of pedestrian footpaths.
\\
Procedural modeling of road networks and even entire cities is of interest to the fields of urban planning and urban architecture.
In recent years there has been an advent of interactive tools that aid urban planners in placing or generating features of an urban plan, particularly roads and road networks.
These tools are created with the purpose of aiding urban planners by giving them increased visualization capabilities, and the ability to quickly perform editing both in the large scale and small scale, and quickly view the results.
Specifically, there have been an advent of tools that exract geodata from OpenStreetMap (OSM) and generate 3D representations of real world locations by placing terrain, buildings, roads and other features.
However, freely available such tools seldom include smaller roads and pedestrian footpaths such as walkways, sidewalks or trails.
\\
This project assesses the feasibility of creating such a service, by focusing on OSM road and building data in the Stockholm metropolitan area.
An estimate of the positional accuracy of OSM data has been obtained by comparing OSM positional data to a dataset with a known accuracy, which was obtained from the Swedish National Land Survey.
This estimate of the positional error was used to assess the integrity of the OSM Stockholm road network, by locating critical points where supplying the roads and paths with indivdual widths would cause collision with other features.
An algortitm then took the road network and made adjustments that were within the found margin of error for the OSM dataset, to eliminate as many collisions as possible.
As secondary contributions, the completeness and shape accuracy of the OSM data set have also been estimated and commented.
\\
It was found that the average positional error in the OSM dataset was about 2m, and approximately 98\% of all buildings in the reference dataset were represented in the OSM dataset.
The report concludes with a discussion of the findings of this study, and an assessment of the feasibility of generating city models with pedestrian footpaths in a number of different applications from urban planning tools to videogames.

@@

% TODO: building match figures in a horisontal grid
% TODO: figure with buildings-slu-cropped
% TODO: mention utility buildings inside compounds, source of marginal errors

% TODO: Scrape road data with same coords as the large data run
% TODO: Organize large building and road datasets
% TODO: Script that imports both building and road data
% TODO: Reconstruct geometrical hashmap to take both polygons and lines
% TODO: Implement new geometrical hashmap in new script
% TODO: Assign default path widths (min)
% TODO: Per road, go over narby features and infer max width, log collisions (max width - min width)

\begin{figure}[H]
\centering
\includegraphics[height=0.5\textheight]{img_turn_function_diff_filled}
\caption{An example of the turning functions of two corresponding buildings, with the area between them highlighted.}
\label{fig:space}
\end{figure}
